A quantitative framework for investigating the reliability of network construction

### 2018-02-07 manuscript/CI_interactions.tex
fixed the and between equations

\author{Alyssa R. Cirtwill$^{1}$, Dominique Gravel$^{2}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{x,y}$, Kate Wootton$^{x}$}
\date{\small$^1$Department of Physics, Chemistry\\ 
and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\

\small$^2$ Département de biologie\\ 
Université de Sherbrooke\\ 
Sherbrooke, Canada\\

\medskip $^x$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
\medskip $^y$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
% \medskip
% $^\dagger$ Corresponding author:\\
% alyssa.cirtwill@gmail.com\\
% +46 723 158464\\
}

@@

      \noindent and

>>>>

\author{Alyssa R. Cirtwill$^{1}$, Dominique Gravel$^{2}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{3,4}$, Kate Wootton$^{3}$}
\date{\small$^1$Department of Physics, Chemistry\\ 
and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
\medskip$^2$ Département de biologie\\ 
Université de Sherbrooke\\ 
Sherbrooke, Canada\\ 
\medskip $^3$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
\medskip $^4$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
% \medskip
% $^\dagger$ Corresponding author:\\
% alyssa.cirtwill@gmail.com\\
% +46 723 158464\\
}

@@
